
---
output: github_document
---

```{r, echo = FALSE, results = "hide", messages = FALSE, warnings = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE)
options(xtable.comment = FALSE)
library(rmarkdown)
library(data.table)
library(ggplot2)
library(ggrepel)
```

Performance Comparisons of Nonlinear Solver
====================

This is part of an ongoing project at university, where I try to find
efficient ways to solve large nonlinear systems. More exactly, large
nonlinear systems that may originate from a CGE (Computable General
Equilibrium) Model in economics.


```{r readin, results='hide', message=FALSE, echo=FALSE}
pcres <- fread("PerfComp_results.csv", fill = TRUE)
pcres.names <- c("Program", "Mode", "Convergence", "Residual", "Problemsize",
                 "Iterations", "NumberProcesses", "Duration", "Options")
setnames(pcres, names(pcres), pcres.names)
pcres[, NumberProcesses := as.factor(NumberProcesses)]

pcres[, Solver := str_extract(Options, "newton..")]

pcres[, Options := NULL]
## View(pcres[Residual < 0.01, ])
## pcres <- pcres[Residual < 0.01, ]

pcres.mean <- pcres[, lapply(.SD, mean),
                    by = .(Program, Mode, Problemsize, NumberProcesses,
                           Solver),
                    .SDcols = c("Duration", "Residual", "Iterations")]
```

```{r firstPlot, echo=FALSE, message=FALSE, results='hide', fig.width=8.5, fig.height=6}
p <- ggplot(pcres.mean, aes(x = Problemsize, y = Duration))
p <- p + geom_line(aes(colour = NumberProcesses, lineType = Solver),
                   size = 1)
p <- p + geom_label_repel(data = pcres.mean[Problemsize == 3000, ],
                          aes(label = Solver), #fill = Program),
                              fontface = "bold",
                          color = "black")
p <- p + scale_x_continuous(breaks = pcres.mean[, unique(Problemsize)])
p <- p + ggtitle("Performance of different software implementations")
p <- p + theme(legend.position = "bottom")
p
```

With $n = 4000$, the parallel version has trouble to find the right
step-size (with the Newton line search solver), but the Newton trust
region solver is slightly faster.
